Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-02-17 scripts/04_downstream_analysis.Rmd
ENH Starting downstream analysis

---
title: "Clustering: A pipeline to analyse time-course gene expression data"
output: rmarkdown::html_vignette
---

```{r echo=FALSE, results="hide"}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)

@@

# Right now, the package doesn't contain the normalized data
pvalues = read.table(".results/pvalues.txt", sep="\t", check.names=FALSE)
```

# Clustering of time-course data

```{r}
if(filter_genes){
    # First, filter out any genes that doesn't have a log fold change of at
    # least 2
    # XXX I should actually filter on the max, but it is broken right now.
    lfc_col_to_keep = colnames(pvalues)[
	grepl("-lfc_max", colnames(pvalues))]
    pvalues = pvalues[rowSums(abs(pvalues[, lfc_col_to_keep]) > 2) > 0, ]

    if(dim(pvalues)[1] > n_genes_to_keep){

	# Then rank by fisher's p-value and take max the number of genes of
	# interest
	# Filter out q-values for the pvalues table
	pval_col_to_keep = colnames(pvalues)[grepl("-pval", colnames(pvalues))]
	pvalues = pvalues[, pval_col_to_keep]
	fishers_pval = moanin:::fisher_method(pvalues)
    } else {
	genes_to_keep = names(pvalues)
    }
    genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])
    y = as.matrix(data[genes_to_keep, ])
}else{
    y = as.matrix(data)
}

#############################################################################
# Fit the splines

kmeans_clusters = moanin::splines_kmeans(
    y, meta, n_clusters=20,
    random_seed=42,
    degrees_of_freedom=df)

# Rescale the centroids
centroids = moanin:::rescale_values(kmeans_clusters$centroids, meta)
all_scores = data.frame(row.names=row.names(data))
for(k in 1:n_clusters){
    scores = moanin:::score_genes_centroid(data, centroids[k,])
    all_scores[paste0("cluster_", k)] = scores
}

# Only assign labels to X% of the genes
max_score = quantile(moanin:::row_min(all_scores), c(percentage_genes_to_label))
genes_to_not_consider = moanin:::row_min(all_scores) >= max_score
labels = moanin:::row_argmin(all_scores)
labels[genes_to_not_consider] = NA
```

```{r}
table(labels)
```

```{r fig.height=8, fig.width=8}

moanin::plot_centroids(centroids, meta)
```

```{r results="hide", echo=FALSE}
# Save the clustering for the next step
write.table(labels, ".results/clustering_labels.txt", sep="\t")
```

>>>>

---
title: "Downstream analysis: A pipeline to analyse time-course gene expression data"
output: rmarkdown::html_vignette
---

```{r echo=FALSE, results="hide"}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)
library(KEGGprofile)

@@

labels = read.table(".results/clustering_labels.txt", sep="\t",
		    check.names=FALSE)
```

### Finding enriched pathways

```{r}
clusters = as.vector(unlist(unique(labels)))
for(cluster in clusters){
    genes = row.names(labels[labels == cluster])
    pathways = KEGGprofile::find_enriched_pathway(
	genes, species="mmu", download_latest=TRUE)
}
```
